---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries,message=FALSE}
# Set up any libraries you need
library(tidyverse)
library(rvest)
library(polite)
library(cancensus)
library(haven)
library(lubridate)
```

# Loading client data

```{r}
# Load all client related Rds files
cust_dev = read_rds("data-raw/cust_dev.Rds")
customer = read_rds("data-raw/customer.Rds")
cust_sleep = read_rds("data-raw/cust_sleep.Rds")
device = read_rds("data-raw/device.Rds")
```

# Getting external data

## Web scraping industry data

```{r}
# Scraping the industry data
url <- "https://fitnesstrackerinfohub.netlify.app/"

# Get scrap target, provide relevant contact information
target <- bow(url,
              user_agent = "jiahao.bai@mail.utoronto.ca",
              force = TRUE)

# Any details provided in the robots text on crawl delays and 
# which agents are allowed to scrape
target

# Obtain data, and convert to data frame
html <- scrape(target)
device_data <- html %>% 
  html_elements("table") %>% 
  html_table() %>% 
  pluck(1)
```

# Census API

```{r, message=FALSE}
# Scraping census data
options(cancensus.api_key = "CensusMapper_b041be566f3982329277d23be6e52e8d",
        cancensus.cache_path = "cache") 


# get all regions as at the 2016 Census (2020 not up yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% 
  as_census_region_list()

# Get the household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD', geo_format = "sf")

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)

```

# Postal code

```{r}
# Load postal code data
dataset = read_rds("data-raw/break_glass_in_case_of_emergency.Rds")

postcode <- dataset %>% 
  select(PC, CSDuid)
```

# Data Merging and Cleaning

## Customer Data

```{r, message=FALSE}
# Join customer data and device data 
customer_new = customer %>% left_join(cust_dev, by = "cust_id") %>% 
               left_join(device, by = "dev_id")

# Postcode
postcode_new = postcode %>% distinct(PC, .keep_all = TRUE) %>% 
               left_join(median_income, by = "CSDuid")

# Merge customer and postcode data
customer_new = customer_new %>% 
               left_join(postcode_new, by = c("postcode" = "PC"))

# Remove unnecessary columns and NA/Intersex customer data, 
# calculate customers age, delete date of birth data
customer_final = customer_new %>% 
                 select(-pronouns, -dev_id, -postcode, -released) %>% 
                 filter(sex %in% c("Female", "Male")) %>% 
                 mutate(age = 2022 - as.numeric(substr(dob, 1, 4))) %>% 
                 select(-dob)

# Rescale ages and household median incomes
customer_final = customer_final %>% 
                 mutate(age_scaled = age, income_scaled = hhld_median_inc)

min_age = min(customer_final$age)
max_age = max(customer_final$age)
customer_final$age_scaled = (customer_final$age - min_age) / 
                            (max_age - min_age)

min_inc = min(customer_final$hhld_median_inc)
max_inc = max(customer_final$hhld_median_inc)
customer_final$income_scaled = (customer_final$hhld_median_inc - min_inc) / 
                               (max_inc - min_inc)

# Check number of distinct emoji modifiers, create new column to represent
# different skin color, and remove emoji_modifier.
unique(customer_final$emoji_modifier) # 6 distinct emoji modifiers in total

customer_final = customer_final %>% 
                 mutate(skinColor = case_when(
                            emoji_modifier == "U+1F3FF" ~ "Dark",
                            is.na(emoji_modifier) ~ "Default",
                            emoji_modifier == "U+1F3FD" ~ "Medium",
                            emoji_modifier == "U+1F3FC" ~ "Medium-light",
                            emoji_modifier == "U+1F3FB" ~ "Light",
                            emoji_modifier == "U+1F3FE" ~ "Medium-dark")) %>% 
                 select(-emoji_modifier)
```

## Customer Sleep Data
```{r}
# Merge customer and customer sleep data
sleep_data = cust_sleep %>% left_join(customer_new, by = "cust_id") %>% 
             mutate(age = 2022 - as.numeric(substr(dob, 1, 4))) %>% 
             filter(sex %in% c("Female", "Male")) %>% 
             select(-pronouns, -dev_id, -postcode, -released, -dob, 
                    -Population, -date) %>% 
             mutate(skinColor = case_when(
                            emoji_modifier == "U+1F3FF" ~ "Dark",
                            is.na(emoji_modifier) ~ "Default",
                            emoji_modifier == "U+1F3FD" ~ "Medium",
                            emoji_modifier == "U+1F3FC" ~ "Medium-light",
                            emoji_modifier == "U+1F3FB" ~ "Light",
                            emoji_modifier == "U+1F3FE" ~ "Medium-dark")) %>% 
             select(-emoji_modifier)

# Rescale ages and household median incomes
sleep_data = sleep_data %>% 
             mutate(age_scaled = scales::rescale(sleep_data$age),
                    income_scaled = scales::rescale(sleep_data$hhld_median_inc))
```

# Export Data

```{r}
# Export Data to data folder
write_rds(customer_final, "data/customer_data.Rds")
write_rds(sleep_data, "data/customer_sleep_data.Rds")
```
























